Working title: Ecological network control

### 2018-05-18 paper/manuscript.Rmd
Swap inaccessible and dilations in figure 1

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right). In this network, the width of the links correspond to the frequency of visitation. We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence. For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$. (b) A system is structurally controllable if there are no inaccessible links or dilations. The network on the bottom left is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system. The network in the bottom right is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```

>>>>

```{r fig-example-networks, fig.width=fig_struct_control$width, fig.height=fig_struct_control$height, fig.cap="(a) To establish the direction of control we start with a weighted visitation network (on the right). In this network, the width of the links correspond to the frequency of visitation. We then calculate the dependencies between species pairs and create a directed network (left) in which the direction of the links correspond to the direction of the assymetry of their dependence. For instance, the population of plant $p_1$ is likely to be affected by the population of pollinator $a_1$ to a larger extent that the population of $a_1$ depends on $p_1$ because $a_1$ interacts more strongly with other species in the community; hence the direction of control between these two species can be simplyfied with a directed link from $a_1$ to $p_1$. (b) A system is structurally controllable if there are no inaccessible links or dilations. The network on the bottom left is not controllable because there is a dilation in which node $x_2$ is being used to control two nodes simultaneously. The network in the bottom right  is not controllable because node $x_3$ is inaccessible from the input node $u_1$ in the system. Both systems can be made controllable by adding an extra input node (top)."}
replayPlot(fig_struct_control$plot)
```
